Formulating and Validating RDF Constraints Generically

### 2014-12-28 paper/paper 2/paper 2.tex
ideas

%
%
\title{XXXXX}
%
\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{XXXXX\inst{1} \and XXXXX\inst{2}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{XXXXX\\
\email{XXXXX},\\ 
\and
XXXXX \\
\email{XXXXX} 
}

@@

\section{Notes}

\begin{itemize}
	\item requirements / constraints mapped to DL
	\item requirements / constraints which cannot be mapped to DL
	\item syntactic sugar for some constraints
	\item complex constraints encompass complex constraints and simple constraints
	\item DL statements of complex constraints are created out of DL statements of composed constraints 
	\item define terminology for RDF constraints
\end{itemize}

@@

Our \textbf{contributions} of this paper are:
\begin{enumerate}
	\item each constraint (expressed by any DSCL) can be validated automatically
	\item any specific constraint (expressed by any DSCL) can be transformed into a generic constraint (expressed by a generic constraint language)
	\item we developed an ontology describing any constraint language
\end{enumerate}

@@

idea:
\begin{itemize}
	\item each specific constraint expressed using any domain specific language can be expressed as DL constraint using DL
	\item each DL constraint can be expressed as generic constraint using generic constraint language
	\item meta-model based ontology describing constraints
	\item possible limitation: maybe only typical constraints
\end{itemize}

purpose:
\begin{itemize}
	\item translations of constraints expressed using any domain specific constraint language
\end{itemize}

contributions:
\begin{itemize}
	\item 
\end{itemize}

assumption:
\begin{itemize}
	\item CWA
\end{itemize}

ontology design pattern.org
constraint grammar
constraint elements are the same
DSP uses other design pattern / 
constraint / constraint elements / constraint design patterns / constraint language
define terminology
related to requirements DB / relate requirements to constraints, constraint languages
constraint element: e.g. min cardinality
dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
min car more powerful than req. propery
why ontology? automatic translation from DSP to OWL 
define general constraint language
we do not invent a new constraint languages
requirements in SPARQL umsetzten
only one validation for each requirement
constraints may be composed

\begin{itemize}
	\item any specific constraint (expressed by DSCL) must be mapped to a generic constraint (expressed by GCL)
\end{itemize}

\section{An Ontology Describing Constraint Languages}

We developed an ontology to describe any constraint language.
We distinguish between two sub-types of \ms{constraint}: 
\begin{itemize}
	\item \ms{property constraints} and 
	\item \ms{class constraints}. 
\end{itemize}

@@

@@

@@

\begin{itemize}
  \item domain and range
	\item (ir)reflexive object properties
	\item Exact Qualified Cardinality Restrictions on Properties
\end{itemize}

@@

>>>>

%
%
\title{Formulating and Validating RDF Constraints Generically}
%\subtitle{}
%
\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Thomas Bosch\inst{1} \and X\inst{2} \and X\inst{2} \and X\inst{2} \and Kai Eckert\inst{2}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
\email{thomas.bosch@gesis.org},\\ 
\and
University of Mannheim, Germany \\
\email{\{kai\}@informatik.uni-mannheim.de} 
}

@@

\begin{itemize}
	\item requirements database
	\item relationship between requirements and constraints
\end{itemize}

\begin{itemize}
	\item the majority of specific constraints expressed by any specific constraint language can be expressed by DL
	\item each DL statement can be expressed by a generic constraint using a generic constraint language
\end{itemize}

purpose:
\begin{itemize}
	\item translations of specific constraints expressed by any specific constraint language
	\item we do not invent a new constraint languages
\end{itemize}

%constraint design patterns:
% - ontology design pattern.org
% - DSP uses other design pattern
% - constraint elements are the same / 
% - constraint / constraint elements / constraint design patterns / constraint language

%dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
%min car more powerful than req. propery

\begin{itemize}
	\item any specific constraint (expressed by specific constraint language) must be mapped to a generic constraint (expressed by GCL)
\end{itemize}

@@

Our \textbf{contributions} of this paper are:
\begin{itemize}
	\item each constraint (expressed by any DSCL) can be validated automatically
	\item any specific constraint (expressed by any DSCL) can be transformed into a generic constraint (expressed by a generic constraint language)
	\item We define the terminology for RDF constraints
	\item we developed an ontology describing any constraint language
\end{itemize}

@@

\section{An Ontology Describing RDF Constraints Generically}

We developed a very simple ontology (three classes, three object properties, and three data properties) which is universal enough to describe any RDF constraint expressible by any RDF constraint language.
We distinguish between two sub-types of \ms{constraint}: 
\begin{itemize}
	\item \ms{property constraints} and 
	\item \ms{class constraints}. 
\end{itemize}

@@

Complex constraints encompass complex constraints and simple constraints.
DL statements of complex constraints are created out of DL statements of composed constraints.

@@

\begin{itemize}
	\item syntactic sugar for some constraints
\end{itemize}

@@

\begin{itemize}
  \item domain and range
	\item Primary Key Properties
	\item (ir)reflexive object properties
	\item Exact Qualified Cardinality Restrictions on Properties
\end{itemize}

\section{Constraints Expressible in DL}

@@

\section{Implementation}

\section{Limitations}

\begin{itemize}
	\item in order to transform specific constraint languages, there must be a concrete syntax in RDF
\end{itemize}

\section{Related Work}

\section{Conclusion and Future Work}
